### 2019-09-01 reports/thesis/chapters/5_inference.tex

Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design had already been done. \texttt{RankFilters} contain implementations of filters such as the mean filter and median filter. The implementation uses multiple threads, each thread filters a row in parallel. This was done by the following, a thread copies the value of each pixels in its current and neighbouring rows into a cache. Then for each column, the thread does calculations using the cache then replaces the pixel value of the image to be filtered with the resulting calculation. Once the row has been filtered, the thread then moves onto the next unfiltered row. Rows in the cache not needed are overwritten with more recent rows.

>>>>

Because the empirical null filter was implemented by modifying the existing code in the class \texttt{RankFilters}, most of the design had already been done. \texttt{RankFilters} contain implementations of filters such as the mean filter and median filter. The implementation uses multiple threads, each thread filters a row in parallel.
